Risk Perceptions for Wearable Devices

### 2015-03-07 tex-inputs/results-regression.tex
More orphans dead.

We created several models using two independent variables as predictors: data and recipient. Because the device (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these five  from our models, which resulted in a total of 72 types of data shared with 4 possible recipients. We also used collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score. For each model, we performed Wald's test to examine the model effects attributable to each of these parameters. The only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other. Thus, we opted to remove the other covariates from our analysis. Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit). As can be seen, the data type was the strongest predictor of VUR. The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression-apx}.

@@

The associated risks for each data type fell into the following five categories:
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\bf Financial:} the loss of money or property.
\item {\bf Image:} the loss of control over one's self-image (e.g., publicizing something embarrassing).
\item {\bf Medical:} the disclosure of medical information.
\item {\bf Physical:} physical harm to the user.
\item {\bf Relationships:} damage to the user's inter-personal relationships.
\end{enumerate}

After independently coding, the researchers met to resolve any disagreements, such that the results reflect unanimity. There was  83\% agreement prior to resolution. Cohen's $\kappa$ was 0.81 for the data categories and 0.75 for the  risks categories, both indicating ``excellent'' agreement~\cite{Fleiss2003}.

With regard to data types, the most concerning type of data was video (78.0\%), which was ranked similarly to photos (76.2\%). Next were audio (66.8\%) and demographic data (65.4\%), followed by behavioral (53.1\%) and biometric (46.3\%) data. We suspect that demographic data was more concerning than we expected because we included information such as a Social Security Number, bank account information, and other financial information. We chose to categorize them as such as they are not biological measurements of the user, nor the other types of data types in our categories. We were very surprised that biometric information was seen as relatively benign  compared to the other broad categories of data. One hypothesis is that since most home users do not use biometric authentication, they may have an inaccurate understanding of the types of systems that might be at risk if biometric data were to be stolen and abused.

With regard to presented risks, we observed that average VURs were highest for financial information disclosure (82.0\%). Information regarding relationships (69.2\%), physical safety (66.4\%), and self-image (65.8\%) followed next in VURs. VURs were lowest for medical information disclosure (47.4\%). One reason why medical risks were ranked relatively low is that this category broadly covered scenarios involving data about the user's health, but also related basic information, such as age, gender, and emotional state. As mentioned in Section \ref{sec:datatypes}, participants saw these as publicly observable and unconcerning.

\begin{table}[t]
\centering
\begin{tabular}{|l| r| r| r|}
\hline
Parameters & $\chi^2$ & $df$ & QIC\\
\hline
\hline
(Intercept) & 442.66 & 1 & 12,727.42\\
Risk & 405.18 & 4 & \\
\hline
(Intercept) & 380.39 & 1 & 12,681.86\\
Data Category & 439.45 & 5 & \\
\hline
(Intercept) & 256.15 & 1 & 12,061.87\\
Risk & 157.84 & 4 & \\
Data Category & 183.90 & 5 & \\
Risk $\times$ Data Category & 259.81 & 8 & \\
\hline
(Intercept) & 62.65 & 1 & 10,406.35\\
Risk & 205.21 & 4 & \\
Data Category & 250.35 & 5 & \\
Recipient & 546.89 & 3 & \\
IUIPC (covariate) & 103.94 & 1 & \\
Gender (covariate) & 9.80 & 1 & \\
IUIPC $\times$ Gender & 8.21 & 1 & \\
Risk $\times$ Data Category & 303.44 & 8 & \\
Recipient $\times$ Risk & 39.14 & 12 & \\
\hline
\end{tabular}
\caption{Goodness-of-fit metrics for additional binary logistic models of our data using general estimating equations to account for repeated measures. The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model. Each parameter listed was statistically significant at $p<0.005$.}
\label{regression2}
\end{table}

>>>>

We created several models using two independent variables as predictors: data and recipient. Because the device (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these five  from our models, which resulted in a total of 72 types of data shared with 4 possible recipients. We also used collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score. For each model, we performed Wald's test to examine the model effects attributable to each of these parameters. The only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other. Thus, we opted to remove the other covariates from our analysis. Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection that also accounts for complexity (lower relative values indicate better fit). As can be seen, the data type was the strongest predictor of VUR. The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression-apx}.

@@

The risks for each data type fell into the following categories:
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\bf Financial:} the loss of money or property.
\item {\bf Image:} the loss of control over one's self-image (e.g., publicizing something embarrassing).
\item {\bf Medical:} the disclosure of medical information.
\item {\bf Physical:} physical harm to the user.
\item {\bf Relationships:} damage to the user's inter-personal relationships.
\end{enumerate}

After independently coding, the researchers met to resolve any disagreements, such that the results reflect unanimity. There was  83\% agreement prior to resolution. Cohen's $\kappa$ was 0.81 for the data categories and 0.75 for the  risk categories, both indicating ``excellent'' agreement~\cite{Fleiss2003}.

With regard to data types, the most concerning type of data was video (78.0\%), which was ranked similarly to photos (76.2\%). Next were audio (66.8\%) and demographic data (65.4\%), followed by behavioral (53.1\%) and biometric (46.3\%) data. We suspect that demographic data was more concerning because it included information such as a Social Security Number, bank account information, and other financial information. We chose to categorize them as such as they are non-biological descriptors of the user. We were very surprised that biometric information was seen as relatively benign compared to the other broad categories of data. One hypothesis is that since most home users do not use biometric authentication, they may have an inaccurate understanding of the types of systems that might be at risk if biometric data are stolen and abused.

With regard to the presented risks, we observed that average VURs were highest for financial information disclosure (82.0\%). Information regarding relationships (69.2\%), physical safety (66.4\%), and self-image (65.8\%) followed. VURs were lowest for medical information disclosure (47.4\%). One reason why medical risks were ranked relatively low is that this category broadly covered scenarios involving data about the user's health, but also included more basic medical information, such as age, gender, and emotional state. As mentioned in Section \ref{sec:datatypes}, participants saw these as publicly observable and unconcerning.

\begin{table}[t]
\centering
\begin{tabular}{|l| r| r| r|}
\hline
Parameters & $\chi^2$ & $df$ & QIC\\
\hline
\hline
(Intercept) & 442.66 & 1 & 12,727.42\\
Risk & 405.18 & 4 & \\
\hline
(Intercept) & 380.39 & 1 & 12,681.86\\
Data Category & 439.45 & 5 & \\
\hline
(Intercept) & 256.15 & 1 & 12,061.87\\
Risk & 157.84 & 4 & \\
Data Category & 183.90 & 5 & \\
Risk $\times$ Data Category & 259.81 & 8 & \\
\hline
(Intercept) & 62.65 & 1 & 10,406.35\\
Risk & 205.21 & 4 & \\
Data Category & 250.35 & 5 & \\
Recipient & 546.89 & 3 & \\
IUIPC (covariate) & 103.94 & 1 & \\
Gender (covariate) & 9.80 & 1 & \\
IUIPC $\times$ Gender & 8.21 & 1 & \\
Risk $\times$ Data Category & 303.44 & 8 & \\
Recipient $\times$ Risk & 39.14 & 12 & \\
\hline
\end{tabular}
\caption{Metrics for additional binary logistic models of our data using general estimating equations to account for repeated measures. The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model. Each parameter listed was statistically significant at $p<0.005$.}
\label{regression2}
\end{table}
